Gaia's constraints on the extremely massive ($\sim$$150\,M_\odot$) runaway star candidate VFTS682

### 2018-06-20 VFTS682_APJL.tex
added mention of X-rays

@@

%of $137.8^{+27.5}_ {-15.9}\Msun$, an apparent age of $1.0^{+0.2}_{-0.2}$\,Myr and an inferred initial mass of $150.0^{+28.7}_{-17.4}\Msun$.  Further parameters of are summarized in Table~\ref{X}.
VFTS682 is relatively isolated in \emph{Spitzer} images, except for the extended
source S10 interpreted as star formation triggered by the wind of
VFTS682 itself by \cite{walborn:13}. In X-rays
\todo{questions: does 682 show excess X-rays (wind collisions?)}

@@

 \begin{acknowledgements}
   \small
   We are grateful to S.\,Torres and M.\,C.\,Ramirez-Tannus
   % and C.\,J.\,Evans
   for help and discussions, European Unions Horizon 2020 research and innovation programme from the European Research Council (ERC), Grant agreement No. 715063 [SdM], the NRC-Canada Plaskett Fellowship [VHB].

>>>>

\cite{townsley:06} did not find
an X-ray point source at the position of VFTS682 in their
\emph{Chandra} survey of the region, which suggests the absence of
colliding winds that would be expected in the presence of companions
even for extreme mass ratios, given the extremely large mass of VFTS682.

@@

%of $137.8^{+27.5}_ {-15.9}\Msun$, an apparent age of $1.0^{+0.2}_{-0.2}$\,Myr and an inferred initial mass of $150.0^{+28.7}_{-17.4}\Msun$.  Further parameters of are summarized in Table~\ref{X}.
VFTS682 is relatively isolated in \emph{Spitzer} images, except for the extended
source S10 interpreted as star formation triggered by the wind of
VFTS682 itself by \cite{walborn:13}.

@@

 \begin{acknowledgements}
   \small
   We are grateful to M.\,C.\,Ramirez-Tannus, S.~N.~Shore, and S.\,Torres
   % and C.\,J.\,Evans
   for help and discussions, European Unions Horizon 2020 research and innovation programme from the European Research Council (ERC), Grant agreement No. 715063 [SdM], the NRC-Canada Plaskett Fellowship [VHB].
